Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2024-11-13 verification.tex
Full draft + edits

Section \ref{sec:msr-vv} identified salt flow-induced \gls{DNP} drift and the strong coupling
between neutronics and thermal-hydraulics as two critical multiphysics interactions that must be
accurately modeled in \gls{MSR} simulation software. This chapter describes Moltres and
subsequently presents several \gls{VV} results and analyses for verifying and validating specific
modeling capabilities in Moltres which relate to the aforementioned multiphysics interactions.
Section \ref{sec:moltres-description} details the neutronics, thermal-hydraulics, and multiphysics
coupling schemes in Moltres for \gls{MSR} multiphysics simulations. Following the model
descriptions, the section also summarizes and assesses previous \gls{MSR} analyses
performed with Moltres. Section \ref{sec:cnrs-benchmark} presents verification results from Moltres
for the CNRS benchmark study. Section \ref{sec:msre-pump} presents key findings from a
collaborative \gls{VV} study based on the \gls{MSRE} pump transient tests conducted in the 1960s.
Section \ref{sec:turbulence} describes the \gls{SA} turbulence model implementation in
Moltres and presents the model \gls{VV} results against common wall-bounded turbulent flow case
studies from literature.

@@

Lastly, this chapter presented the implementation and verification of the \gls{SA} model
\cite{spalart_one-equation_1994} in Moltres for enabling wall-bounded turbulent molten salt flow
modeling. The \gls{SA} model includes a rotation correction scheme
\cite{aupoix_extensions_2003, dacles-mariani_numericalexperimental_1995} for improved accuracy when
modeling turbulent flow with curved streamlines. The \gls{SA} model performed well under the
turbulent channel flow verification test \cite{moser_direct_1999}, the turbulent pipe flow
validation test \cite{laufer_structure_1954}, and the \gls{BFS} flow validation test
\cite{driver_features_1985}.

>>>>

Section \ref{sec:msr-vv} identified salt flow-induced \gls{DNP} drift and the strong coupling
between neutronics and thermal-hydraulics as two critical multiphysics interactions that must be
accurately modeled in \gls{MSR} simulation software. This chapter describes Moltres and
subsequently presents several \gls{VV} results and analyses for verifying and validating specific
modeling capabilities in Moltres which relate to the aforementioned multiphysics interactions.
Section \ref{sec:moltres-description} details the neutronics, thermal-hydraulics, and multiphysics
coupling schemes in Moltres for \gls{MSR} multiphysics simulations. Following the model
descriptions, the section also summarizes and assesses previous \gls{MSR} analyses
performed with Moltres. Section \ref{sec:cnrs-benchmark} presents verification results from Moltres
for the CNRS benchmark study. Section \ref{sec:msre-pump} presents key findings from a
collaborative \gls{VV} study based on the \gls{MSRE} pump transient tests conducted in the 1960s.
Section \ref{sec:turbulence} describes the Spalart-Allmaras turbulence model implementation in
Moltres and presents the model \gls{VV} results against common wall-bounded turbulent flow case
studies from literature.

@@

Lastly, this chapter presented the implementation and verification of the Spalart-Allmaras model
\cite{spalart_one-equation_1994} in Moltres for enabling wall-bounded turbulent molten salt flow
modeling. The Spalart-Allmaras model includes a rotation correction scheme
\cite{aupoix_extensions_2003, dacles-mariani_numericalexperimental_1995} for improved accuracy when
modeling turbulent flow with curved streamlines. The Spalart-Allmaras model performed well under the
turbulent channel flow verification test \cite{moser_direct_1999}, the turbulent pipe flow
validation test \cite{laufer_structure_1954}, and the \gls{BFS} flow validation test
\cite{driver_features_1985}.
